Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2020-07-31 Manuscript/HI_Model_ms.Rmd
updated manuscript files

The wildfire transition sub-model was modified from @daniel_state-and-transition_2016 using a new wildfire spatial database for the Hawaiian Islands from 1999-2019 (Figure S4). Wildfire size distribution and ignition probabilities for each year were calculated from this 21-year time series for each unique combination of moisture zone (Figure S1), island, and state type (Figure 1). The number and size of fires was randomly drawn from one of these historical year-sets for each timestep and Monte Carlo realization. Wildfire in the low land-use scenario was sampled from the subset of historical fire years at or below the 21-year median area burned statewide, and the high land-use scenario sampled from historical fire years above this 21-year median (Fig. S4a). Burn severity probabilities (high, medium, low) for each combination of moisture zone and state type were taken from @selmants_baseline_2017. Wildfire transitions were restricted to previously burned areas using a map of all wildfires from 1999-2018.

>>>>

The wildfire transition sub-model was modified from @daniel_state-and-transition_2016 using a new wildfire spatial database for the Hawaiian Islands from 1999-2019 (Figure S4). Wildfire size distribution and ignition probabilities for each year were calculated from this 21-year time series for each unique combination of moisture zone (Figure S1), island, and state type (Figure 1). The number and size of fires was randomly drawn from one of these historical year-sets for each timestep and Monte Carlo realization, using burn severity probabilities from @selmants_baseline_2017. Wildfire in the low land-use scenario was sampled from the subset of historical fire years at or below the 21-year median area burned statewide and the high land-use scenario sampled from historical fire years above this 21-year median (Fig. S4a).

Tree plantation harvesting
